Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-06-01 mu/article/article.tex
ChWS

\blindtext
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \caption{Up structure}
    \label{fig:up-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \caption{Alt structure.}
    \label{fig:alt-struc}
\end{figure}
\blindtext
\blindtext

\blindtext

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \caption{Up structure}
    \label{fig:up-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \caption{Alt structure.}
    \label{fig:alt-struc}
\end{figure}

Since its discovery, graphene has attracted a great interest in materials
science and condensed matter physics being a new class of materials that are
only one atom thick\cite{geimNM07}. This allotrope of carbon with hexagonal
lattice structure is almost transparent and presents properties like fractional
quantum Hall effect at room temperature, excellent thermal transport properties,
high conductivity and strength.\cite{geimNM07, reinaNL08, novoselov2S07,
balandinNL08} Presenting a metallic band structure the band gap can be opened by changing the surface area\cite{hanPRL07}
